Order statistics and numerical optimization

### 2019-11-20 inst/collusion_chess_draws.Rnw
fixes #23

<<kka_equal_strength, print=FALSE,echo=FALSE>>=
objective <- function(V){
  x <- V[1]  # strength of all three players
  w <- V[2]  # white player advantage
  D <- 1-3*x-w  # Draw monster
  return(  
      -loglik(karpov_kasparov_anand,c(x,x,x,w))  # negative as we minimize
  )
}

@@

    return(  
        -loglik(kka_3draws,
                c(karpov,kasparov,anand,white,draw,draw)
                )
        )
}

>>>>

<<kka_equal_strength, print=FALSE,echo=FALSE>>=
objective <- function(V){
  x <- V[1]  # strength of all three players
  w <- V[2]  # white player advantage
  D <- 1-3*x-w  # Draw monster
  return(  
      -loglik(c(x,x,x,w),karpov_kasparov_anand)  # negative as we minimize
  )
}

@@

    return(  
        -loglik(
                c(karpov,kasparov,anand,white,draw,draw),
             kka_3draws
                )
        )
}

### 2019-11-20 inst/cook.Rmd
look at finding the loser
fixes #23

```{r} 
L1 <- loglik(H,indep(equalp(H)))  # support at equal strengths
L2 <- loglik(H,indep(maxp(H)))    # maximum support
L2-L1
pchisq(2*(L2-L1),df=1,lower.tail=FALSE) # p-value of asymptotic distribution
```

@@

```{r}
library(partitions)
imH <- indep(maxp(H))
f <- function(o){loglik(order_likelihood(o),imH,log=FALSE)}
LL <- apply(perms(5),2,f)
length(LL)
sum(LL)
head(LL)
```

>>>>

```{r} 
L1 <- loglik(indep(equalp(H)),H)  # support at equal strengths
L2 <- loglik(indep(maxp(H)),H)    # maximum support
L2-L1
pchisq(2*(L2-L1),df=1,lower.tail=FALSE) # p-value of asymptotic distribution
```

@@

```{r}
library(partitions)
imH <- indep(maxp(H))
f <- function(o){loglik(imH,order_likelihood(o),log=FALSE)}
LL <- apply(perms(5),2,f)
length(LL)
sum(LL)
head(LL)
```

### 2019-11-20 inst/order.Rmd
fixes #23

```{r}
evaluate1 <- maxp(H)
(maxlike1 <- loglik(H,indep(evaluate1)))
dotchart(evaluate1,pch=16)
```

@@

```{r}
f <- function(p,n){c(p,rep((1-p)/n,n-1))}
sss <- f(0.9999,9)  # sensible start point, close (?) to the evaluate
evaluate2 <- maxp(H,startp=sss)
maxlike2 <- loglik(H,indep(evaluate2))
```

@@

```{r}
evaluate3 <- maxp(H,vsssp(4,10))
maxlike3 <- loglik(H,indep(evaluate3))
dotchart(evaluate3,pch=16)
```

>>>>

```{r}
evaluate1 <- maxp(H)
(maxlike1 <- loglik(indep(evaluate1),H))
dotchart(evaluate1,pch=16)
```

@@

```{r}
f <- function(p,n){c(p,rep((1-p)/n,n-1))}
sss <- f(0.9999,9)  # sensible start point, close (?) to the evaluate
evaluate2 <- maxp(H,startp=sss)
maxlike2 <- loglik(indep(evaluate2),H)
```

@@

```{r}
evaluate3 <- maxp(H,vsssp(4,10))
maxlike3 <- loglik(indep(evaluate3),H)
dotchart(evaluate3,pch=16)
```
